MATH 3969 - Measure Theory and Fourier Analysis \\ Exam Notes

### 2011-12-16 MATH 3964 - Complex Analysis/MATH 3964 Lecture Notes.tex
Added hyperref package to generate links within PDFs
fixed rakefile

\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Ga}{\mathbb{G}}

@@

@@

\begin{defn}
	A function $f(z)$ is \textbf{analytic} on a region $D$ if it is differentiable everywhere on $D$.  Thus the derivative $f'(z)$ is a function defined on $D$.  a function is analytic at a particular point $z_0 \in \C$ if it is differentiable on some open neighbourhood of $z_0$.
\end{defn}

@@

\begin{defn}[Analyticitiy at infinity]
	Suppose that $f(z)$ is analytic on an unbounded set and let $g(z) = f(1/z)$.  Then the point $\infty \in \C^{\star}$ is  point of analyticity of $f(z)$ if $z=0$ is a point of analyticity of $g(z)$.  Similarly, $z = \infty$ is a singularity of a particular type of $f(z)$ if $g(z)$ has a singularity of that same type at $z=0$. 
\end{defn}

@@

\begin{defn}
	A function is \textbf{meromorphic} if it is analytic in the whole complex plane $\C$ except for poles.  
\end{defn}

@@

\begin{defn}[Singular points of differential equations and their solutions]
	Consider the $\nth$-order differential equation,\[
		w^{(n)} = f(z, w, w', w'', \dots, w^{(n-1)})
	\] where $f$ is a locally analytic function of its $n$ complex arguments.  A singular point of the differential equation is a point \[
		(z_0, w_0, w'_0, \dots, w_0^{(n-1)}) \in \C^n
	\]
	at which $f$ is \textbf{not analytic} or a point where one or more of the arguments is \textbf{infinite}.

@@

We have an integral formula \[
	F(\alpha, \beta; \gamma; z) = \frac{\Gamma(\gamma)}{\Gamma(\gamma - \beta)\Gamma(\beta)} \int_0^1 t^{\beta - 1} (1-t)^{\gamma - \beta - 1} (1- zt)^{- \alpha} \,dt
\] valid for $\Re \gamma > \Re \beta > 0$, $|z| < 1$. but can be extended to $z \in \C = [1,\infty)$.

@@

\begin{thm}
	The transcendental equation $f(z) = a$ where $f(z)$ is an elliptic function of order $m$ has exactly $m$ roots in every period parallelogram, counting multiplicities, for every $a \in \C$.  
\end{thm}

>>>>

\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Com}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Ga}{\mathbb{G}}

@@

\usepackage{hyperref}

@@

\begin{defn}
	A function $f(z)$ is \textbf{analytic} on a region $D$ if it is differentiable everywhere on $D$.  Thus the derivative $f'(z)$ is a function defined on $D$.  a function is analytic at a particular point $z_0 \in \Com$ if it is differentiable on some open neighbourhood of $z_0$.
\end{defn}

@@

\begin{defn}[Analyticitiy at infinity]
	Suppose that $f(z)$ is analytic on an unbounded set and let $g(z) = f(1/z)$.  Then the point $\infty \in \Com^{\star}$ is  point of analyticity of $f(z)$ if $z=0$ is a point of analyticity of $g(z)$.  Similarly, $z = \infty$ is a singularity of a particular type of $f(z)$ if $g(z)$ has a singularity of that same type at $z=0$. 
\end{defn}

@@

\begin{defn}
	A function is \textbf{meromorphic} if it is analytic in the whole complex plane $\Com$ except for poles.  
\end{defn}

@@

\begin{defn}[Singular points of differential equations and their solutions]
	Consider the $\nth$-order differential equation,\[
		w^{(n)} = f(z, w, w', w'', \dots, w^{(n-1)})
	\] where $f$ is a locally analytic function of its $n$ complex arguments.  A singular point of the differential equation is a point \[
		(z_0, w_0, w'_0, \dots, w_0^{(n-1)}) \in \Com^n
	\]
	at which $f$ is \textbf{not analytic} or a point where one or more of the arguments is \textbf{infinite}.

@@

We have an integral formula \[
	F(\alpha, \beta; \gamma; z) = \frac{\Gamma(\gamma)}{\Gamma(\gamma - \beta)\Gamma(\beta)} \int_0^1 t^{\beta - 1} (1-t)^{\gamma - \beta - 1} (1- zt)^{- \alpha} \,dt
\] valid for $\Re \gamma > \Re \beta > 0$, $|z| < 1$. but can be extended to $z \in \Com = [1,\infty)$.

@@

\begin{thm}
	The transcendental equation $f(z) = a$ where $f(z)$ is an elliptic function of order $m$ has exactly $m$ roots in every period parallelogram, counting multiplicities, for every $a \in \Com$.  
\end{thm}

### 2011-12-16 MATH 3969 - Measure Theory and Fourier Analysis/MATH 3969 Lecture Notes.tex
Added hyperref package to generate links within PDFs
fixed rakefile

\newcommand{\al}{\alpha}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Ga}{\mathbb{G}}

@@

\begin{defn}[Translation of a function]
 	Let $f: \R^N \rightarrow \C$ be a function and $t \in \R^N$ a fixed vector. We define the translation operator $\tau_t$ by \[
 		\tau_t f(x) = f(x-t)
 	\]
\end{defn}

@@

\begin{lem}
	Let $f : \R^N \rightarrow \C$ be measurable and set 
	\begin{align*}
		F_1(x,y) &= f(x) \\
		F_2(x,y) &= f(y-x)
	\end{align*}

	Then $F_1, F_2 : \R^N \times \R^N \rightarrow \C$ are measurable.
\end{lem}

\begin{defn}[Convolution]
	Let $f,g : \R^N \rightarrow \C$ be measurable.  We define the \textbf{convolution} $f \star g : \R^N \rightarrow \C$ by \[
		(f \star g) (x) = \int_{\R^N} f(x-y) g(y) \, dy
	\]
	wherever the integral exists
\end{defn}

@@

\begin{thm}[Young's inequality]
	Let $1 \leq p \leq \infty$.  If $f \in L^p(\R^N, \C)$ and $g \in L^1(\R^N, \C)$, then $f \star g$ exists almost everywhere and $f \star g \in L^p(\R^N, \C)$.  Moverover, \[
		\|f \star g \|_p \leq \|f\|_p \|g \|_1
	\]
\end{thm}

@@

\begin{defn}[Fourier transform]
	Let $f \in L^1(\R^N, \C)$.  We call \[
		\hat{f}(t) = \int_{\R^N} f(x) e^{-2 \pi i x \cdot t} \, dx
	\]
\end{defn}

\begin{thm}
	We have 
	\begin{itemize}
		\item $\hat{f} : \R^N \rightarrow \C$ is continuous,
		\item $\|\hat f \|_\infty \leq \|f \|_1$
	\end{itemize}
\end{thm}

@@

\begin{prop}
	Let $f \in L^1(\R^N, \C), x_0 \in \R^N$ and $\alpha \in R, \alpha > 0$. 
	\begin{enumerate}[(i)]
		\item If $g(x) = f(x - x_0)$, then $\hat g (t) = e^{-2 \pi i x_0 \cdot t} \hat f (t)$,
		\item If $g(x) = f(\alpha x)$, then $\hat g (t) = \frac{1}{\alpha^N} \hat f \left( \frac{x}{\alpha}\right)$,
		\item \vspace{0.1cm} If $g(x) = \overline{f(-x)}$, then $\hat g (t) = \overline{\hat f(t)}$
	\end{enumerate}
\end{prop}

@@

\begin{thm}[Riemann-Lebesgue]
	If $f \in L^1(\R^N, \C)$, then $\hat f \in C_0(\R^N, \C)$ and $\| \hat f \|_\infty \leq \|f \|_1$.
\end{thm}

\begin{thm}
	If $f,g \in L^1(\R^N, \C)$ then $f \star g \in L^1(\R^N, \C)$ and \[
		\hat{f \star g} = \hat f \, \hat g
	\]
\end{thm}
\begin{prop}
	Let $f,g \in L^1(\R^N, \C)$.  Then \[
		\int_{\R^N} \hat f g \, dx = \int_{\R^N} f \hat g \, dx
	\]
\end{prop}

\begin{lem}
	Let $\phi(x) = e^{- \pi |x|^2}$ and $\phi_n(x) = n^N \phi(n x)$.  Then \[
		\int_{\R^N} \hat f (t) e^{2 \pi i x \cdot t} \phi\left(\frac{t}{n} \right) \, dt = (f \star \phi_n) (x)
	\]
	for all $f \in L^1(\R^N,\C), x \in \R^N$, and $n \in \mathbb{N}$.
\end{lem}

\begin{thm}[Fourier inversion formula]
	Let $f \in L^1(\R^N, \C)$. Then 
	\begin{enumerate}[(i)]
		\item \[
			\lim_{n \rightarrow \infty} \int_{\R^N} \hat f (t) e^{2 \pi i x \cdot t} e^{- \pi \frac{|t|^2}{n^2}} \, dt = f
		\] in $L^1(\R^N, \C)$.
		\item If $f$ is continuous at $x$, then \[
			\lim_{n \rightarrow \infty} \int_{\R^N} \hat f (t) e^{2 \pi i x \cdot t} e^{- \pi \frac{|t|^2}{n^2}} \, dt = f(x)
		\]
	\end{enumerate}
\end{thm}

@@

\begin{thm}
	Let $f \in L^2(\R^N, \C)$.  Then \[
		\lim_{n \rightarrow \infty} \int_{\R^N} \hat f (t) e^{2 \pi i x \cdot t} e^{- \pi \frac{|t|^2}{n^2}} \, dt = f
	\] in $L^2(\R^N, \C)$.
\end{thm}

>>>>

\newcommand{\al}{\alpha}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Com}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Ga}{\mathbb{G}}

@@

\begin{defn}[Translation of a function]
 	Let $f: \R^N \rightarrow \Com$ be a function and $t \in \R^N$ a fixed vector. We define the translation operator $\tau_t$ by \[
 		\tau_t f(x) = f(x-t)
 	\]
\end{defn}

@@

\begin{lem}
	Let $f : \R^N \rightarrow \Com$ be measurable and set 
	\begin{align*}
		F_1(x,y) &= f(x) \\
		F_2(x,y) &= f(y-x)
	\end{align*}

	Then $F_1, F_2 : \R^N \times \R^N \rightarrow \Com$ are measurable.
\end{lem}

\begin{defn}[Convolution]
	Let $f,g : \R^N \rightarrow \Com$ be measurable.  We define the \textbf{convolution} $f \star g : \R^N \rightarrow \Com$ by \[
		(f \star g) (x) = \int_{\R^N} f(x-y) g(y) \, dy
	\]
	wherever the integral exists
\end{defn}

@@

\begin{thm}[Young's inequality]
	Let $1 \leq p \leq \infty$.  If $f \in L^p(\R^N, \Com)$ and $g \in L^1(\R^N, \Com)$, then $f \star g$ exists almost everywhere and $f \star g \in L^p(\R^N, \Com)$.  Moverover, \[
		\|f \star g \|_p \leq \|f\|_p \|g \|_1
	\]
\end{thm}

@@

\begin{defn}[Fourier transform]
	Let $f \in L^1(\R^N, \Com)$.  We call \[
		\hat{f}(t) = \int_{\R^N} f(x) e^{-2 \pi i x \cdot t} \, dx
	\]
\end{defn}

\begin{thm}
	We have 
	\begin{itemize}
		\item $\hat{f} : \R^N \rightarrow \Com$ is continuous,
		\item $\|\hat f \|_\infty \leq \|f \|_1$
	\end{itemize}
\end{thm}

@@

\begin{prop}
	Let $f \in L^1(\R^N, \Com), x_0 \in \R^N$ and $\alpha \in R, \alpha > 0$. 
	\begin{enumerate}[(i)]
		\item If $g(x) = f(x - x_0)$, then $\hat g (t) = e^{-2 \pi i x_0 \cdot t} \hat f (t)$,
		\item If $g(x) = f(\alpha x)$, then $\hat g (t) = \frac{1}{\alpha^N} \hat f \left( \frac{x}{\alpha}\right)$,
		\item \vspace{0.1cm} If $g(x) = \overline{f(-x)}$, then $\hat g (t) = \overline{\hat f(t)}$
	\end{enumerate}
\end{prop}

@@

\begin{thm}[Riemann-Lebesgue]
	If $f \in L^1(\R^N, \Com)$, then $\hat f \in C_0(\R^N, \Com)$ and $\| \hat f \|_\infty \leq \|f \|_1$.
\end{thm}

\begin{thm}
	If $f,g \in L^1(\R^N, \Com)$ then $f \star g \in L^1(\R^N, \Com)$ and \[
		\hat{f \star g} = \hat f \, \hat g
	\]
\end{thm}
\begin{prop}
	Let $f,g \in L^1(\R^N, \Com)$.  Then \[
		\int_{\R^N} \hat f g \, dx = \int_{\R^N} f \hat g \, dx
	\]
\end{prop}

\begin{lem}
	Let $\phi(x) = e^{- \pi |x|^2}$ and $\phi_n(x) = n^N \phi(n x)$.  Then \[
		\int_{\R^N} \hat f (t) e^{2 \pi i x \cdot t} \phi\left(\frac{t}{n} \right) \, dt = (f \star \phi_n) (x)
	\]
	for all $f \in L^1(\R^N,\Com), x \in \R^N$, and $n \in \mathbb{N}$.
\end{lem}

\begin{thm}[Fourier inversion formula]
	Let $f \in L^1(\R^N, \Com)$. Then 
	\begin{enumerate}[(i)]
		\item \[
			\lim_{n \rightarrow \infty} \int_{\R^N} \hat f (t) e^{2 \pi i x \cdot t} e^{- \pi \frac{|t|^2}{n^2}} \, dt = f
		\] in $L^1(\R^N, \Com)$.
		\item If $f$ is continuous at $x$, then \[
			\lim_{n \rightarrow \infty} \int_{\R^N} \hat f (t) e^{2 \pi i x \cdot t} e^{- \pi \frac{|t|^2}{n^2}} \, dt = f(x)
		\]
	\end{enumerate}
\end{thm}

@@

\begin{thm}
	Let $f \in L^2(\R^N, \Com)$.  Then \[
		\lim_{n \rightarrow \infty} \int_{\R^N} \hat f (t) e^{2 \pi i x \cdot t} e^{- \pi \frac{|t|^2}{n^2}} \, dt = f
	\] in $L^2(\R^N, \Com)$.
\end{thm}
